---
title: "Lab: Linear Regression"
author: "Your Name"
date: 'Last Compiled: `r format(Sys.time(), "%b %d, %Y")`'
#bibliography: PackagesUsedRegression.bib
output: 
  bookdown::html_document2: 
    highlight: textmate
    theme: yeti
---


```{r, label = "SETUP", echo = FALSE, results= 'hide', message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(comment = NA, fig.align = 'center', fig.height = 5, fig.width = 5, prompt = FALSE, highlight = TRUE, tidy = FALSE, warning = FALSE, message = FALSE, tidy.opts=list(blank = TRUE, width.cutoff = 80))
```


# Libraries

The `library()` function is used to load libraries, or groups of functions and data sets that are not included in the base `R` distribution. Basic functions that perform least squares linear regression and other simple analyses come standard with the base distribution, but more exotic functions require additional libraries. Here we load the `MASS` package, which is a very large collection of data sets and functions. We also load the `ISLR` package, which includes the data sets associated with this book.

```{r}
library(MASS)
library(ISLR)
library(DT)
```

If you receive an error message when loading any of these libraries, it likely indicates that the corresponding library has not yet been installed on your system. Some libraries, such as `MASS`, come with `R` and do not need to be separately installed on your computer. However, other packages, such as `ISLR`, must be downloaded the first time they are used. This can be done directly from within `R`. For example, on a Windows system, select the Install package option under the Packages tab. After you select any mirror site, a list of available packages will appear. Simply select the package you wish to install and `R` will automatically download the package. Alternatively, this can be done at the `R` command line via `install.packages("ISLR")`. This installation only needs to be done the first time you use a package. However, the `library()` function must be called each time you wish to use a given package.

# Simple Linear Regression

The `MASS` library contains the Boston data set, which records medv (median house value) for 506 neighborhoods around Boston. We will seek to predict medv using 13 predictors such as `rm` (average number of rooms per house), `age` (average age of houses), and `lstat` (percent of households with low socioeconomic status).

```{r}
names(Boston)
datatable(Boston, rownames = FALSE)
```

To find out more about the data set, we can type `?Boston`.

